An Adolescent Mini-Neptune in the Kepler Field

### 2021-08-07 paper/ms.tex
update ms

% paragraph 1: HR 
To assess the age of the cluster as well as our star of interest,
we used a combination of the isochronal, gyrochronal, and
lithium-based age-dating.

@@

Kinematics are reasonably compelling
(Appendix~\ref{app:kinematicselection}).
HR diagram in and of itself doesn't give any age information about the
star.   (Could quote funny literature isochrone ages).
Rotation is informative, and is consistent with cluster.
Final point: Lithium.  Quote your EW. 
All together, pretty good.  We adopt the age based on the pre-main-sequence
empirical fitting procedure from Section~\ref{sec:cmd}:
$35^{+6}_{-5}$\, Myr.

%FIXME FIXME FIXME
From the ensemble perspective, which
provides the strongest constraints (SEE CITET SODERBLOM 2014), the age
of the star is $XX \pm YY$\,Myr.  Individual measurements of the
star's rotation period and lithium abundance corroborate this
conclusion.

@@

If the \pn\ transit signal is created by a bonafide planet, this age
would make it the youngest planet yet found by the main Kepler
mission\footnote{The re-purposed K2 mission found two slightly younger
systems: K2-33b \citep{David_et_al_2017,Mann_K2_33b_2016} and V1298
Tau \citep{david_four_2019}}.  A portion of the light curve is shown
with the phase-folded transit
in Figure~\ref{fig:lc}.  The dominant signal in the
\texttt{PDCSAP} photometry is a quasi-period starspot signal with a
peak-to-peak amplitude that varies between roughly 2\% and 8\%,
depending on the degree of asymmetry in spot coverage between the
stellar hemispheres.  The starspot signal repeats every
$2.642\pm0.042$\,days, where we have adopted an uncertainty based on
the scatter observed between different portions (quarters) of the
time-series data.  The details of how we model this starspot signal to
derive the parameters of the planet are discussed in
Appendix~\ref{app:gptransit}.  The results, given in
Table~\ref{tab:posterior}, are consistent with a mini-Neptune sized
planet ($3.56\pm 0.04\,R_\oplus$) on a circular 7.2\,day orbit
($e<0.XX$), around a G8V star ($0.91 \pm 0.05 R_\odot$).  {\bf TODO
quote the eccentricity limit}

>>>>

% paragraph 1: HR 
To assess the age of the cluster and our star of interest,
we used a combination of the isochronal, gyrochronal, and
lithium-based age-dating.

@@

To summarize, the age of the \cn\ cluster based on the empirical
fitting procedure described in Section~\ref{sec:cmd} is
$35^{+6}_{-5}$\, Myr.  This procedure hinges on the age adopted
for IC\,2602, since it is the closest reference cluster in the color-magnitude diagram.
Gyrochronologically, while most of the G and K
dwarfs in the \cn\ have not yet converged to form a slow sequence,
their rotation distribution and that of the F dwarfs is consistent
with the same age.  The rotation periods of other
30\,Myr to 50\,Myr clusters ({\it e.g.}, IC\,2602, Collinder 135)
are indistinguishable
(S.~Douglas, priv{.}~comm{.}).  The most precise age for \sn\ and its
planet are therefore also $35^{+6}_{-5}$\, Myr, based on the star's spatial,
kinematic, and rotational connection to this larger ensemble, and the assumption that
\pn\ formed very quickly after the star itself.

% TODO:  update this based on HIRES instead of TRES
% TODO:  cite Stephanie instead of priv comm? Send her your Prot
Beyond the kinematic and rotational lines of evidence for the youth of \sn,
there is a final consistency check: the abundance of Li\,\textsc{I} as
inferred from the 6708\,\AA\ doublet.  This connection of this element
to age measurements for young stars has been reviewed by
\citet{soderblom_ages_2014}.  Following the equivalent width
measurement procedure described by \citet{bouma_2021_ngc2516}, we find
${\rm EW}_{\rm Li} = 232^{+23}_{-13}\,$m\AA, which does not
correct for the Fe\,\textsc{I} blend at 6707.44\AA\.  Given $T_{\rm eff} \approx
5500\,{\rm K}$, this measurement is also in agreement with an age for
the star between 30\,Myr and 50\,Myr (see {\it e.g.}, Figure~9 of
\citealt{bouma_2021_ngc2516}, or the data
from \citealt{randich_gaiaeso_2018}).

@@

If the \pn\ transit signal is created by a bonafide planet,  then to
our knowledge its age would make it the youngest planet yet found by
the main Kepler mission\footnote{The re-purposed K2 mission found two
slightly younger systems: K2-33b
\citep{David_et_al_2017,Mann_K2_33b_2016} and V1298 Tau
\citep{david_four_2019}}.  A portion of the light curve is shown with
the phase-folded transit in Figure~\ref{fig:lc}.  The dominant signal
in the \texttt{PDCSAP} photometry is a quasi-periodic starspot signal
with a peak-to-peak amplitude that varies between roughly 2\% and 8\%,
depending on the degree of asymmetry in spot coverage between the
stellar hemispheres.  The starspot signal repeats every
$2.642\pm0.042$\,days, where we have adopted an uncertainty based on
the scatter observed between different portions (quarters) of the
time-series data.  The details of how we model this starspot signal to
derive the parameters of the planet are discussed in
Appendix~\ref{app:gptransit}.  The results, given in
Table~\ref{tab:posterior}, are consistent with a mini-Neptune sized
planet ($3.56\pm 0.04\,R_\oplus$) on a circular 7.2\,day orbit
($e<0.XX$), around a G8V star ($0.91 \pm 0.05 R_\odot$).  {\bf TODO
quote the eccentricity limit}
